### 2018-03-11 paper/5-implementations.tex
Rename ask to fetch, in agreement with Andrey

\begin{minted}{haskell}
shake :: Hashable v => Build Monad [Trace k v] k v
shake = recursive $ \k _ ask act -> do
    poss <- traceMatch (\k v -> (==) v . getHash <$> ask k) k =<< getInfo
    h <- getStoreHash k
    when (h `notElem` poss) $ do
        (dk, v) <- act
        putStore k v
        dh <- mapM getStoreHash dk
        modifyInfo (Trace k (zip dk dh) (getHash v) :)
\end{minted}

This implementation uses the \hs{recursive} function which requires a function which gets the key to build (\hs{k}), a way to ask for the result of a dependecy (\hs{ask}), and a way to build \hs{k} (\hs{act}). The code first looks up the traces that match the current situation, creating a list of possible results as \hs{poss}, using the helper \hs{traceMatch}. We check if the current value for the key is one of the possible results, and it not, build the key and store it in the trace. We can implement \hs{traceMatch}, which is used in all build systems working with \hs{Trace}, as:

@@

\begin{minted}{haskell}
recursive
    :: (m ~ M i k v, Default i)
    => (k -> Maybe [k] -> (k -> m v) -> m ([k], v) -> m ())
    -> Build Monad i k v
recursive step compute = runM . ensure
    where
        ensure k = do
            let ask x = ensure x >> getStore x
            done <- getTemp
            when (k `Set.notMember` done) $ do
                modifyTemp $ Set.insert k set
                case trackDependencies compute ask k of
                    Nothing -> return ()
                    Just act -> step k (getDependenciesMaybe compute k) ask act
\end{minted}

@@

\begin{minted}{haskell}
cloudShake :: Hashable v => Build Monad (Traces k v) k v
cloudShake = recursive $ \k _ ask act -> do
    poss <- traceMatch (\k v -> (== v) . getHash <$> ask k) k . traces =<< getInfo
    if null poss then do
        (dk, v) <- act
        dh <- mapM getStoreHash dk
        modifyInfo $ \i -> i
            {traces = Trace k (zip dk dh) (getHash v) : traces i
            ,contents = Map.insert (getHash v) v $ contents i}
        putStore k v
    else do
        now <- getStoreHash k
        when (now `notElem` poss) $
            putStore k . (Map.! head poss) . contents =<< getInfo
\end{minted}

The differences from \hs{bazel} are minor - the dependency scheme has changed from \hs{topological} to \hs{recursive}, and thus the dependency keys \hs{dk} are captured from the action rather than in advance, and the checking calls \hs{ask} to get the result instead of accessing the store directly. We believe this accurately captures and can be used to reason about how to make \Shake work with a cloud-based cache -- a challenge we intend to attempt in the future.

>>>>

\begin{minted}{haskell}
shake :: Hashable v => Build Monad [Trace k v] k v
shake = recursive $ \k _ fetch act -> do
    poss <- traceMatch (\k v -> (==) v . getHash <$> fetch k) k =<< getInfo
    h <- getStoreHash k
    when (h `notElem` poss) $ do
        (dk, v) <- act
        putStore k v
        dh <- mapM getStoreHash dk
        modifyInfo (Trace k (zip dk dh) (getHash v) :)
\end{minted}

This implementation uses the \hs{recursive} function which requires a function which gets the key to build (\hs{k}), a way to fetch the result of a dependecy (\hs{fetch}), and a way to build \hs{k} (\hs{act}). The code first looks up the traces that match the current situation, creating a list of possible results as \hs{poss}, using the helper \hs{traceMatch}. We check if the current value for the key is one of the possible results, and it not, build the key and store it in the trace. We can implement \hs{traceMatch}, which is used in all build systems working with \hs{Trace}, as:

@@

\begin{minted}{haskell}
recursive
    :: (m ~ M i k v, Default i)
    => (k -> Maybe [k] -> (k -> m v) -> m ([k], v) -> m ())
    -> Build Monad i k v
recursive step compute = runM . ensure
    where
        ensure k = do
            let fetch x = ensure x >> getStore x
            done <- getTemp
            when (k `Set.notMember` done) $ do
                modifyTemp $ Set.insert k set
                case trackDependencies compute fetch k of
                    Nothing -> return ()
                    Just act -> step k (getDependenciesMaybe compute k) fetch act
\end{minted}

@@

\begin{minted}{haskell}
cloudShake :: Hashable v => Build Monad (Traces k v) k v
cloudShake = recursive $ \k _ fetch act -> do
    poss <- traceMatch (\k v -> (== v) . getHash <$> fetch k) k . traces =<< getInfo
    if null poss then do
        (dk, v) <- act
        dh <- mapM getStoreHash dk
        modifyInfo $ \i -> i
            {traces = Trace k (zip dk dh) (getHash v) : traces i
            ,contents = Map.insert (getHash v) v $ contents i}
        putStore k v
    else do
        now <- getStoreHash k
        when (now `notElem` poss) $
            putStore k . (Map.! head poss) . contents =<< getInfo
\end{minted}

The differences from \hs{bazel} are minor - the dependency scheme has changed from \hs{topological} to \hs{recursive}, and thus the dependency keys \hs{dk} are captured from the action rather than in advance, and the checking calls \hs{fetch} to get the result instead of accessing the store directly. We believe this accurately captures and can be used to reason about how to make \Shake work with a cloud-based cache -- a challenge we intend to attempt in the future.
